The Astropy Project:

### 2017-09-23 main.tex
Update on Overleaf.
Adding text about release cycle and versioning

\subsection{Long term support of v2.0}
% This could also include information about the development cycle

@@

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
bsipocz may write this up if there is no other takers
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up

>>>>

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
%
% - reference APE2 for versioning and APE10 for dropping python2 support
% - shall we maybe refer to the release calendar, too?
% - should we mention that v3.0 is the exception to the version numbering
%   scheme we use by not being 2.1?
\par The general scheme for the releases and version numbering that the core
package has adopted if the following. Astropy has new feature releases every
6 month, and between feature releases additional bugfix releases that
contain only bugfixes but no new features. The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports Python2, and will receive bug fixes until the
end of 2019.
%
\par The version numbering of astropy reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advances
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.

@@

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
% Brigitta may write this up if there is no other takers
\subsection{Continuous integration helpers}
% Brigitta
\subsection{sphinx extensions}
% Tom R
